On exponential sums arising from the classical doubling method

### 2025-04-21 main.tex
Minor changes

In these cases, the map $i:\algebraicGroup{G} \to \GroupExtension{\algebraicGroup{G}}$ yields a pullback map $i^*:\GroupExtension{\algebraicGroup{G}}^* \to \algebraicGroup{G}^*$ well defined up to composing with an inner automorphism induced by an $\Frobenius$-stable element of the maximal torus. From chasing definitions, one finds

\begin{proposition}[{\cite[Corollary 9.7]{Bonnafe2006}}]
	\label{prop:i*isrestriction}
	$i^*(s_{\algebraicGroup{T},\theta}) = s_{\algebraicGroup{T} \cap G, \theta|_{G}}$.
\end{proposition}

This gives a natural \calvin{check that this is correct} $|\algebraicGroup{Z}(\GroupExtension{\algebraicGroup{G}})(\finiteField)|/|\algebraicGroup{Z}(\algebraicGroup{G}
)(\finiteField)|$-to-one map from Lusztig packets for $\GroupExtension{\algebraicGroup{G}}$ to those for $\algebraicGroup{G}$.

>>>>

In these cases, the map $i:\algebraicGroup{G} \to \GroupExtension{\algebraicGroup{G}}$ yields a pullback map $i^*:\GroupExtension{\algebraicGroup{G}}^* \to \algebraicGroup{G}^*$ well defined up to composing with an inner automorphism induced by an $\Frobenius$-stable element of the maximal torus. From chasing definitions, one finds the following.

\begin{proposition}[{\cite[Corollary 9.7]{Bonnafe2006}}]
	\label{prop:i*isrestriction}
	$i^*(s_{\algebraicGroup{T},\theta}) = s_{\algebraicGroup{T} \cap G, \theta\restriction_{\algebraicGroup{T} \cap G}}$.
\end{proposition}

This gives a natural \calvin{check that this is correct} $|\algebraicGroup{Z}(\GroupExtension{\algebraicGroup{G}})(\finiteField)|/|\algebraicGroup{Z}(\algebraicGroup{G}
)(\finiteField)|$-to-one map from geometric Lusztig series for $\GroupExtension{\algebraicGroup{G}}$ to those for $\algebraicGroup{G}$.
